supplementary

### 2021-12-10 products/manuscript/Manuscript.Rmd
Final update!

_Results:_

@@

## Questions/Hypotheses to be addressed
The main question is to find out the key factors associated with covid-19 testing

@@

_**Study design, sample, and procedure**_

@@

_**Measures**_
Using Andersen’s model of health care utilization , study variables will be categorized into outcome variable, predisposing factors, enabling/disabling factors and need for care factors.

_**Outcome variable**_
COVID-19 testing/infection status will be assessed with the question, “Since the beginning of the COVID-19 outbreak, do you have information on your infection status?” Response options were 1=not tested/does not know test results, 2=negative, and 3=positive.

_**Predisposing factors**_
Sociodemographic factors included age, sex, country of residence, educational level, and the (estimated) age(s) of their housemate(s). Chronic/underlying diseases includs heart disease, hypertension, diabetes, cancer, HIV, tuberculosis, and chronic asthma; coded as “0” none and “1” at least presence of one clinically diagnosed condition.

_**COVID-19 preventive measures**_
Participants were asked, “During the past 7 days, have you been observing any of the following preventive measures against COVID-19? 1) Social distancing of at least 1.5m, 2) Wearing a face mask, 3) Hand hygiene (regular handwashing with soap or using hand gel), and 4) Coughing hygiene (covering the mouth when coughing or sneezing). A composite non-adherence to all four COVID-19 preventive measure was calculated by coding each negative response with “1”, summing scores ranging from 0-4 (Cronbach’s alpha 0.7).

_**Enabling factors**_
Enabling factors include self-perceived socio-economic status, self-perceived area of residence, being a student or worker in the health care sector, source of COVID-19 information/advice most trusted (coded as other, including family and friends, radio/TV, social media, religious authorities and health personnel[@Bono].

_**Need for care factors**_ include two questions on 1) the level of fear/worry of being infected with COVID-19 (ranging from 1=not at all worried to 5=extremely worried), and 2) having been quarantined (either at home or elsewhere) at any point in time during the COVID-19 epidemic.

_**Data analysis**_

@@

## Data aquisition
_As applicable, explain where and how you got the data. If you directly import the data from an online source, you can combine this section with the next._

## Data import and cleaning_ html_document
---
```{r}
library(here)
```
## Exploratory analysis

```{r summarytable,  echo=FALSE}
resulttable=readRDS("../../results/Overall.rds")
knitr::kable(resulttable, caption = "**Overall Descriptive Statistics of the Participants**")
```

As the infection status information of the participants is the main outcome variable, let's see its distribution among the participants:

```{r resultfigure,  fig.cap='Infection Status Information.', echo=FALSE}
knitr::include_graphics("../../results/infection_status_info_distribution.png")
```

Among the participants, **78.9%** are less than or equal  to 35 years old. That indicates that majority of the participants tend to be younger. While **45.18%** of the participants were female, **54.82%** were male, which shows less chance of biad due to sex. **78.05%** of the participants had a bachelor or post-bachelor degree, clearly indicating that majority of the participants had pretty good education background. Almost **50%** of the participants belongs to "upper middle income category", indicating that at least half of the participants don't belong to the poorer side. Less than **10%** of the participants live in a village/rural area. Health professionals and Tv/radio seems to be the most trusted source to the participants. Apparently equal half of the participants worked from home or not at some stage of the study. Major half of the participants did quarantine at some stage during the study. **63%** of the participants didn't go through a COVID test. Almost half of the participants **(46%)** were moderate or more worried about reinfection. Only **22%** of the participants recorded to have some sort of chronic disease. **(Separate analysis for each variable was done and the data can be accessed/viewd through the "supplementary.rmd" file)**

Let's look at the logistic regression analysis and its statistics summary between the **outcome variable** (infection status info) and the three key **predisposing factors** (Age, Sex, Education level).
```{r summarytable12,  echo=FALSE}
resulttable=readRDS("../../results/lg_fit_table_predisposing.rds")
knitr::kable(resulttable, caption = "logistic regression betweem infection status and Key Predisposing Factors")
```

@@

Next, we want to see the logistic regression analysis statistics between the **outcome variable** (infection status info) and the three key **enabling factors** (socio economic status, area of residence,student/healthworker, source of covid news).

@@

@@

@@

## Summary and Interpretation
_Summarize what you did, what you found and what it means._

>>>>

**Results:** Of the 759 participants, 37% had tested for COVID-19, 9% tested positive, and 28.0% tested negative. In a logistic regression model, predisposing factors (Age, being female, having at least one chronic condition) and enabling/disabling factors (urban residence, higher perceived economic status) increased the odds of COVID-19 testing. Among those who were tested, participants residing in Bangladesh, those who had moderate to to severe psychological distress were positively associated with COVID-19 positive diagnosis.

@@

## Questions/Hypotheses to be addressed
The main question is to find out the key factors associated with covid-19 testing decision. There are several predisposing factors, enabling factors, disabling factors, need for care factors and we aim to find out which of them significantly plays a role behind an individual's decision to get tested for covid.

@@

_**Study design, sample, and procedure:**_

@@

_**Measures:**_
Using Andersen’s model of health care utilization , study variables will be categorized into outcome variable, predisposing factors, enabling/disabling factors and need for care factors.

_**Outcome variable:**_
COVID-19 testing/infection status will be assessed with the question, “Since the beginning of the COVID-19 outbreak, do you have information on your infection status?” Response options were 1=not tested/does not know test results, 2=negative, and 3=positive.

_**Predisposing factors:**_
Sociodemographic factors included age, sex, country of residence, educational level, and the (estimated) age(s) of their housemate(s). Chronic/underlying diseases includs heart disease, hypertension, diabetes, cancer, HIV, tuberculosis, and chronic asthma; coded as “0” none and “1” at least presence of one clinically diagnosed condition.

_**COVID-19 preventive measures:**_
Participants were asked, “During the past 7 days, have you been observing any of the following preventive measures against COVID-19? 1) Social distancing of at least 1.5m, 2) Wearing a face mask, 3) Hand hygiene (regular handwashing with soap or using hand gel), and 4) Coughing hygiene (covering the mouth when coughing or sneezing). A composite non-adherence to all four COVID-19 preventive measure was calculated by coding each negative response with “1”, summing scores ranging from 0-4 (Cronbach’s alpha 0.7).

_**Enabling factors:**_
Enabling factors include self-perceived socio-economic status, self-perceived area of residence, being a student or worker in the health care sector, source of COVID-19 information/advice most trusted (coded as other, including family and friends, radio/TV, social media, religious authorities and health personnel[@Bono].

_**Need for care factors:**_ include two questions on 1) the level of fear/worry of being infected with COVID-19 (ranging from 1=not at all worried to 5=extremely worried), and 2) having been quarantined (either at home or elsewhere) at any point in time during the COVID-19 epidemic.

_**Data analysis procedure**_

@@

## Data Analysis:
---
First of all, let's have a look at the overall descriptive status of the participants.
```{r}
library(here)
resulttable=readRDS("../../results/Overall.rds")
knitr::kable(resulttable, caption = "**Overall Descriptive Statistics of the Participants**")
```
Among the participants, **78.9%** are less than or equal  to 35 years old. That indicates that majority of the participants tend to be younger. While **45.18%** of the participants were female, **54.82%** were male, which shows less chance of bias due to sex. **78.05%** of the participants had a bachelor or post-bachelor degree, clearly indicating that majority of the participants had pretty good education background. Almost **50%** of the participants belongs to "upper middle income category", indicating that at least half of the participants don't belong to the poorer side. Less than **10%** of the participants live in a village/rural area. Health professionals and Tv/radio seems to be the most trusted source to the participants. Apparently equal half of the participants worked from home or not at some stage of the study. Major half of the participants did quarantine at some stage during the study. **63%** of the participants didn't go through a COVID test. Almost half of the participants **(46%)** were moderate or more worried about reinfection. Only **22%** of the participants recorded to have some sort of chronic disease. **(Separate analysis for each variable was done and the data can be accessed/viewed through the "supplementary.rmd" file)**

As the infection status information of the participants is the _**main outcome variable**_, let's see its distribution among the participants:

```{r resultfigure,  fig.cap='Infection Status Information.', echo=FALSE}
knitr::include_graphics("../../results/infection_status_info_distribution.png")
```
So, among 759 participants, 445 didn't have any test. 197 was tested positive and 64 was tested negative. Clearly, there is major difference in number between the group who have gone through testing and who haven't. Our main focus is to find out which factors are affecting their decision whether they want to get tested or not.

Let's look at the univariate logistic regression analysis and its statistics summary between the **outcome variable** (infection status info) and the three key **predisposing factors** (Age, Sex, Education level).
```{r summarytable12,  echo=FALSE}
resulttable=readRDS("../../results/lg_fit_table_predisposing.rds")
knitr::kable(resulttable, caption = "logistic regression betweem infection status and Key Predisposing Factors")
```

Here, all three predisposing factors (Age, Sex and Education level) seems to have a significant effect on the participants' decision making to get tested or not as the p-values are <0.05. The quality of this model selection has been supported by the statistical data shown below:

@@

Next, we want to see the univariate logistic regression analysis statistics between the **outcome variable** (infection status info) and the three key **enabling factors** (socio economic status, area of residence,student/healthworker, source of covid news).

@@

While, difeerent socio economic status and residence area have strong importance on the testing decision making, the source of their covid information didn't seem to affect their decision making much. The quality of this model selection has been supported by the statistical data shown below:

@@

Their worry level seems to have affect their decision to get tested for covid.The quality of this model selection has been supported by the statistical data shown below:

@@

## Results

In total, 759 participants were included in the study with mean age 30.70 years. Of these 63% had never tested for COVID-19, 28% tested positive and 9.0% tested negative

**Predisposing factor**

One in five participants (20.1%) were 35 years and older, 45.18% were female, 78% had a graduate/postgraduate education, 21.5% had at least one diagnosed chronic/underlying disease, and only 2.1% did not adhere to the any of the four COVID-19 preventive measures.

**Enabling/disabling factors**

Most participants (63.03%) resided in urban areas, 56.0% rated their socio-economic status as upper middle to high-income, and 32% were students or workers in health care. The most trusted source of COVID-19 information/advice was health care personnel (33.5%), 37% had correct COVID-19 knowledge, and 46% reported moderate to severe psychological distress.

**Need for care factors**

More than half of the participants (70.7%) were very or extremely worried about being (re)infected with COVID-19, and 57.64% had been quarantined during the COVID-19 pandemic (see Table 1 and exploratory.rmd).

**Associations**

In the logistic regression model, predisposing factors (Age, Sex, Education Level) and enabling/disabling factors (urban residence, higher perceived economic status, being a student or worker in the health care sector) increased the odds of COVID-19 testing.Also, multivariate logistic regression of the odds of a COVID-19 positive diagnosis among all individuals tested or not tested found that urban residence, higher perceived economic status were positively associated with a COVID-19 positive diagnosis.

### 2021-12-10 products/manuscript/supplementary.Rmd
Final update!

```{r summarytable,  echo=FALSE}
resulttable=readRDS("../../results/summarytable.rds")
knitr::kable(resulttable, caption = 'Age Percentage of Participants.')
```
**78.9% of total participants are less than or equal  to 35 years old.**

```{r summarytable2,  echo=FALSE}
resulttable=readRDS("../../results/summarytable2.rds")
knitr::kable(resulttable, caption = 'Sex Percentage of Participants.')
```
**While 45.18% of the participants were female, 54.82% were male.**

```{r summarytable3,  echo=FALSE}
resulttable=readRDS("../../results/summarytable3.rds")
knitr::kable(resulttable, caption = 'Education Background Percentage of Participants.')
```
**78.05% of the participants had a bachelor or post-bachelor degree**
```{r summarytable4,  echo=FALSE}
resulttable=readRDS("../../results/summarytable4.rds")
knitr::kable(resulttable, caption = 'Income Percentage of Participants.')
```
**Almost 50% of the participants belongs to "upper middle income category"**
```{r summarytable5,  echo=FALSE}
resulttable=readRDS("../../results/summarytable5.rds")
knitr::kable(resulttable, caption = 'Residence Percentage of Participants.')
```
**Less than 10% of the participants live in a village/rural area**
```{r summarytable6,  echo=FALSE}
resulttable=readRDS("../../results/summarytable6.rds")
knitr::kable(resulttable, caption = 'Source of information Percentage of Participants.')
```
**Health professionals and Tv/radio seems to be the most trusted source to the participants.**
```{r summarytable7,  echo=FALSE}
resulttable=readRDS("../../results/summarytable7.rds")
knitr::kable(resulttable, caption = 'Percentage of Participants working from home or not.')
```
**Apparently equal half of the participants worked from or not**
```{r summarytable8,  echo=FALSE}
resulttable=readRDS("../../results/summarytable8.rds")
knitr::kable(resulttable, caption = 'Percentage of Participants quarantined or not at some stage.')
```
**Major half of the participants did quarantine at some stage during the study**
```{r summarytable9,  echo=FALSE}
resulttable=readRDS("../../results/summarytable9.rds")
knitr::kable(resulttable, caption = 'Percentage of covid test status of the participants.')
```
**63% of the participants didn't go through a COVID test**
```{r summarytable10,  echo=FALSE}
resulttable=readRDS("../../results/summarytable10.rds")
knitr::kable(resulttable, caption = "Percentage of participants' worry level about (re)infection with COVID-19.")
```
**Almost half of the participants (46%) were moderate or more worried about reinfection**
```{r summarytable11,  echo=FALSE}
resulttable=readRDS("../../results/summarytable11.rds")
knitr::kable(resulttable, caption = "Percentage of participants' history of chronic disease")
```
**Only 22% of the participants recorded to have some sort of chronic disease**

>>>>

**###I wanted to see the age distribution of the participants.**
```{r summarytable,  echo=FALSE}
resulttable=readRDS("../../results/summarytable.rds")
knitr::kable(resulttable, caption = 'Age Percentage of Participants.')
```
_78.9% of total participants are less than or equal  to 35 years old._

**###Next, I wanted to see the gender distribution of the participants**
```{r summarytable2,  echo=FALSE}
resulttable=readRDS("../../results/summarytable2.rds")
knitr::kable(resulttable, caption = 'Sex Percentage of Participants.')
```
_While 45.18% of the participants were female, 54.82% were male._

**###here, I wanted to see which education background each of the participants possessed**
```{r summarytable3,  echo=FALSE}
resulttable=readRDS("../../results/summarytable3.rds")
knitr::kable(resulttable, caption = 'Education Background Percentage of Participants.')
```
_78.05% of the participants had a bachelor or post-bachelor degree_

**###Now, I want to see which income group each of them belong to**
```{r summarytable4,  echo=FALSE}
resulttable=readRDS("../../results/summarytable4.rds")
knitr::kable(resulttable, caption = 'Income Percentage of Participants.')
```
_Almost 50% of the participants belongs to "upper middle income category"_

**###Where do they live?**
```{r summarytable5,  echo=FALSE}
resulttable=readRDS("../../results/summarytable5.rds")
knitr::kable(resulttable, caption = 'Residence Percentage of Participants.')
```
_Less than 10% of the participants live in a village/rural area_

**###Let's see which source they have been using to get updates about covid**
```{r summarytable6,  echo=FALSE}
resulttable=readRDS("../../results/summarytable6.rds")
knitr::kable(resulttable, caption = 'Source of information Percentage of Participants.')
```
_Health professionals and Tv/radio seems to be the most trusted source to the participants._

**###Are most of them working from home or not? Let's find out**
```{r summarytable7,  echo=FALSE}
resulttable=readRDS("../../results/summarytable7.rds")
knitr::kable(resulttable, caption = 'Percentage of Participants working from home or not.')
```
_Apparently equal half of the participants worked from or not_

**###I wanted to see what proportion of the participants had to undergo quarantine at some stages**
```{r summarytable8,  echo=FALSE}
resulttable=readRDS("../../results/summarytable8.rds")
knitr::kable(resulttable, caption = 'Percentage of Participants quarantined or not at some stage.')
```
_Major half of the participants did quarantine at some stage during the study_

**###What proportion of the participants knew their infection status (positive/negative/no test doen)? This is our primary outcome of interest. So, fiinding this was very important**
```{r summarytable9,  echo=FALSE}
resulttable=readRDS("../../results/summarytable9.rds")
knitr::kable(resulttable, caption = 'Percentage of covid test status of the participants.')
```
_63% of the participants didn't go through a COVID test._

**###What was the worry level of the participants? We divided the cohort in groupd like 'moderrately worried', 'a little worried', 'very worried', 'extremely worried' and 'not at all worried'. Proportion for each group is shown below:**
```{r summarytable10,  echo=FALSE}
resulttable=readRDS("../../results/summarytable10.rds")
knitr::kable(resulttable, caption = "Percentage of participants' worry level about (re)infection with COVID-19.")
```
_Almost half of the participants (46%) were moderate or more worried about reinfection_

**###What percent of participants had some sort of chronic disease history? Let's find out**
```{r summarytable11,  echo=FALSE}
resulttable=readRDS("../../results/summarytable11.rds")
knitr::kable(resulttable, caption = "Percentage of participants' history of chronic disease")
```
_Only 22% of the participants recorded to have some sort of chronic disease_
